Hierarchical Reverberation Mapping

### 2013-09-29 Paper/ms.tex
Figure
scale = 0.5
New figure (CCF), some work on text

There are many subtleties involved in reverberation mapping, that we will ignore
for the purposes of this letter. We note them here for completeness. Firstly,
the lag $\tau$ is not equal to $c$ times the mean radius of the BLR
distribution. Secondly, the lag $\tau$ is also not what the common
cross-correlation techniques measures, except in the case of very narrow
transfer functions (i.e. only a single lag in the system, rather than a wide
distribution of lags). Some of these difficulties have been addressed in other
contributions by \citet{pancoast} and \citet{arp151}.

@@

@@

>>>>

There are many subtleties involved in reverberation mapping, that we will ignore
for the purposes of this letter. We note them here for completeness. Firstly,
the mean lag $\bar{\tau} = \int \Psi(\tau)\, d\tau$, where $\Psi(\tau)$
is the transfer function, is not equal to $c$ times the mean radius of the BLR
distribution. Secondly, the mean lag $\bar{\tau}$ is also not what is measured
by the common
cross-correlation technique, except in the case of very narrow
transfer functions. Direct physical modelling of the BRL resolves these
issues \citep{pancoast, arp151}.

@@

\section{Model Assumptions}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/posterior.eps}
\caption{The joint posterior distribution for $\mu$ and $\sigma$, hyperparameters
describing the distribution of $\bar{\tau}$ values in the sample. The prior
distribution was uniform over the area shown.
The true solution is indicated by the white circle.\label{fig:posterior}}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/ccf.eps}
\caption{The stacked cross-correlation function of the simulated data.
\label{fig:ccf}}
\end{center}
\end{figure}
